\propertitle

### 2019-12-15 maxNt_v6.tex
update

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2019-12-15T19:19:48+0100
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourfalse% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimtrue
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\updated}{\today}
\newcommand*{\firstdraft}{4 November 2015}
\newcommand*{\firstpublished}{***}
\newcommand*{\propertitle}{Inferring the total activity of a large neuronal population\\ from a small sample}
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{Inferences about large neuronal populations}
\newcommand*{\pdfauthor}{P.G.L.  Porta Mana, Y. Roudi, V. Rostami, E. Torre}
\newcommand*{\headauthor}{Porta Mana \etal}
\newcommand*{\reporthead}{}% Report number

@@

\enquote{Cooperativity}, \enquote{interaction}, and similar terms are
vague, so we need to translate them into a more precise notion first. Here
we use the notion of \emph{informational sufficiency}
\citep[\sect~4.5]{bernardoetal1994}[\chap~8 \amp\
\sect~14.2]{jaynes1994_r2003}{cifarellietal1982,kullbacketal1951}[the
notion goes back to][]{fisher1922} because it relates to those terms and
especially because is tightly connected with maximum-entropy distributions.
Its idea is as follows. Our probabilities about the frequencies of the
activities of the sample, or about the activity of the sample in a new time
bin, are in principle conditional on all experimental data and statistics
we have. But it can be the case that discarding part of the data or
statistics -- for example, the third- and higher-order empirical moments --
leaves our probabilities almost unchanged. This means that the discarded
statistics are \emph{informationally irrelevant} or almost so. The
remaining statistics -- for example, first and second empirical moments --
are \emph{informationally sufficient}.\footnote{For more technical results
  and connections with the notion of symmetry see \eg\
  \cite{darmois1935,neyman1935,koopman1936,pitman1936,halmosetal1949,bahadur1954,berk1972,lauritzen1974,lauritzen1982_r1988,lauritzen2007,cifarellietal1980,cifarellietal1981,diaconisetal1981,diaconis1992,furmanczyketal1998,fortinietal2000,nogalesetal2000,kallenberg2005,ayetal2015}.}
% This informational quasi-sufficiency is interesting because
% it may give clues about population organization and dynamics.

This notion is useful in our present problem, owing to its tight connection
with maximum-entropy distributions: \emph{if a probability distribution for
  repetitive phenomena has a sufficient statistics, then it is a mixture of
  distributions of maximum-entropy form}. \mynote{move the following
  somewhere else? }This mathematical result comes from the Pitman-Koopman
theorem\citep{jaynes1982b}[\sect~4.5.4]{bernardoetal1994}
\citep{koopman1936,pitman1936,darmois1935}[for later analyses and the
discrete case
see][]{hipp1974,andersen1970,denny1967,denny1972,fraser1963,barankinetal1963,barndorffnielsen1978_r2014}

>>>>

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2019-12-15T19:33:22+0100
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourfalse% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimtrue
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\updated}{\today}
\newcommand*{\firstdraft}{4 November 2015}
\newcommand*{\firstpublished}{***}
\newcommand*{\propertitle}{Inferring the total activity of a large neuronal population\\ from a small sample}
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{Inferences about large neuronal populations}
\newcommand*{\pdfauthor}{P.G.L.  Porta Mana, Y. Roudi, V. Rostami, E. Torre}
\newcommand*{\headauthor}{Porta Mana \etal}
\newcommand*{\reporthead}{}% Report number

@@

\enquote{Cooperativity}, \enquote{interaction}, and similar terms are
vague, so we need to translate them into a more precise notion first. Here
we use the notion of \emph{informational sufficiency}
\citep[\sect~4.5]{bernardoetal1994}[\chap~8 \amp\
\sect~14.2]{jaynes1994_r2003} because it relates to those terms and
especially because it is tightly connected with maximum-entropy
distributions. We now shortly explain its meaning and use; please see the
end of this section for a bibliography with in-depth discussions.

Our probabilities about the frequencies of the activities of the sample, or
about the activity of the sample in a new time bin, are in principle
conditional on all experimental data and statistics we have. But it can be
the case that discarding part of the data or statistics -- for example, the
third- and higher-order empirical moments -- leaves our probabilities
almost unchanged. This means that the discarded statistics are
\emph{informationally irrelevant} or almost so. The remaining statistics --
for example, first and second empirical moments -- are
\emph{informationally sufficient}.\footnote{For more technical results and
  connections with the notion of symmetry see \eg\
  \cite{darmois1935,neyman1935,koopman1936,pitman1936,halmosetal1949,bahadur1954,berk1972,lauritzen1974,lauritzen1982_r1988,lauritzen2007,cifarellietal1980,cifarellietal1981,diaconisetal1981,diaconis1992,furmanczyketal1998,fortinietal2000,nogalesetal2000,kallenberg2005,ayetal2015}.}
% This informational quasi-sufficiency is interesting because
% it may give clues about population organization and dynamics.

This notion is useful in our present problem, owing to its tight connection
with maximum-entropy distributions: \emph{if a probability distribution for
  repetitive phenomena has a sufficient statistics, then it is a mixture of
  distributions of maximum-entropy form}. \mynote{move the following
  somewhere else? }This mathematical result comes from the Pitman-Koopman
theorem\citep{cifarellietal1982,kullbacketal1951}[the
notion goes back to][]{fisher1922} \citep{jaynes1982b}[\sect~4.5.4]{bernardoetal1994}
\citep{koopman1936,pitman1936,darmois1935}[for later analyses and the
discrete case
see][]{hipp1974,andersen1970,denny1967,denny1972,fraser1963,barankinetal1963,barndorffnielsen1978_r2014}
